Language-Based Security for Low-Level MPC

### 2024-05-17 ppdp24/intro.tex
checkpoint

Program logics for probabilistic languages and specifically reasoning
about properties such as joint probabilistic independence is also
important related work. Probabilistic Separation Logic (PSL)
\cite{barthe2019probabilistic} develops a logical framework for
reasoning about probabilistic independence (aka separation) in
programs, and they consider several (hyper)properties, such as perfect
secrecy of one-time-pads and indistinguishability in secret sharing,
that are critical to MPC. However, their methods are manual, and they
do not capture notions of conditional independence (separation). This
latter issue has been addressed in Lilac \cite{XXX}, but the
application of Lilac-style reasoning to MPC protocols has not
previously been explored, as we do in Section
\ref{section-example-gmw}.

@@

\paragraph{Language design.} In Section \ref{section-minicat} we
develop a new probabilistic programming language $\minifed$ for
defining synchronous distributed protocols over the binary field. The
syntax and semantics provides a succinct account of \emph{views} and
(synchronous) messaging between protocol \emph{clients}. In Section
\ref{section-metalang} we define a new metaprogramming language
$\metaprot$ that dynamically generates $\minifed$ protocols. It
includes control and data structures and is able to express logical
protocol components, and enjoys a type safety result that guarantees
that generated protocols are semantically well-defined.

>>>>

Program logics for probabilistic languages and specifically reasoning
about properties such as joint probabilistic independence is also
important related work. Probabilistic Separation Logic (PSL)
\cite{barthe2019probabilistic} develops a logical framework for
reasoning about probabilistic independence (aka separation) in
programs, and they consider several (hyper)properties, such as perfect
secrecy of one-time-pads and indistinguishability in secret sharing,
that are critical to MPC. However, their methods are manual, and
don't include conditional independence (separation). This
latter issue has been addressed in Lilac \cite{XXX}. The
application of Lilac-style reasoning to MPC protocols has not
previously been explored, as we do in Section
\ref{section-example-gmw}.

@@

\paragraph{Language design.} In Section \ref{section-lang} we
develop a new probabilistic programming language $\minifed$ for
defining synchronous distributed protocols over an arbitrary
arithmetic field. The syntax and semantics provides a succinct account
of synchronous messaging between protocol \emph{clients}. In Section
\ref{section-metalang} we define a metalanguage $\metaprot$ that
dynamically generates $\minifed$ protocols. It is able to express
important low-level abstractions, as we illustrate via implementations
of protocols including Shamir addition (Section \ref{section-lang}),
GMW boolean circuits (Section \ref{section-example-gmw}), and Beaver
Triple multiplication gates with BDOZ authentication (Section
\ref{section-example-bdoz}).
